\bf Title

### 2023-10-26 article/paper_padic_spec.tex
debut sec poly LP

\begin{definition}
  A {\it polyhedron} is a subset $P \subset K^n$ of the form
  $P = \{X \in K^n : \val(\ell_1(X))\geq0,\ldots,\val(\ell_n(X))\geq 0\}$,
  where $\ell_1,\ldots,\ell_d \in K[X]_1$ are affine polynomials on $X = (X_1, \ldots, X_n)$.
\end{definition}

\begin{example}
  The closed unit ball in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the polyhedron defined as
  the set of $(X_1,\ldots,X_n) \in K^n$ such that
  $$
  \begin{pmatrix} x_1 &  & & \\
    & x_2 &0 &  \\
    &  0& \ddots & \\
    &  & & x_s/
  \end{pmatrix} \ge 0.$$ which is in fact $\OK^s$.
\end{example}

@@

A {\it linear programming problem} (or simply {\it linear program}) is
\begin{equation}
  \tag{LP}
  \begin{matrix}
    \text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
    Ax + b \ge 0
  \end{matrix}
  \label{eqn:Proglinp}
\end{equation}

with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fixed a vector of size $m$.

>>>>

\begin{definition}
  A {\it polyhedron} is a subset $P \subset K^n$ of the form
  $P = \{X \in K^n : \val(\ell_1(X))\geq0,\ldots,\val(\ell_n(X))\geq 0\}$,
  for some $\ell_1,\ldots,\ell_d \in K[X]_1$. This will often be denoted with
  the compact notation $\val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0$, where $\val$
  and $\geq$ are applied entrywise.
\end{definition}

\begin{example}
  The closed unit ball $B_\infty(K^n)$ in $K^n$ for the supremum norm $||\cdot||_{\infty}$ is the
  polyhedron defined as the set of $X=(X_1,\ldots,X_n) \in K^n$ such that $||X||_{\infty} =
  \max_i\{X_i\}\leq 1$, other words, such that $\val(X_i) \geq 0$, for all $i=1, \ldots, n$.
  In other words, $\OK^n = B_\infty(K^n)$ is the polyhedron in $K^n$ defined by the affine polynomials
  $\ell_i(X)=X_i$, $i=1,\ldots, n$.
%  $$
%  \begin{pmatrix} x_1 &  & & \\
%    & x_2 &0 &  \\
%    &  0& \ddots & \\
%    &  & & x_s/
  %  \end{pmatrix} \ge 0.$$
\end{example}

@@

A {\it linear programming problem} (or simply {\it linear program}) is given by the following
optimization problem:
\begin{equation}
  \tag{LP}
\begin{array}{rcll}
  p^* & := & \inf_{X \in \R^n} & \val(\left\langle c, X \right\rangle) \\
  &    & \text{s.t.}         & A X + b \geq 0
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost, $A \in \allmat_{m,n}(K)$ and $b \in K^m$.
